---
title: "Analyses_Manuscript"
author: "Jens H. Fünderich"
format: html
editor: visual
---

# Set Up

## Install & Load packages

```{r}

## Library Loading
packages <- c("brms", 
              "cmdstanr",
              "flextable",
              "ggplot2",
              "dplyr",
              "officer",
              "osfr",
              "readr", 
              "rmarkdown")

## install.packages("systemfonts") I had to install this, so flextable would work, you may not have to
## it fixed this error: 
# Error: package or namespace load failed for ‘flextable’: 
# object ‘match_fonts’ is not exported by 'namespace:systemfonts'

## check, whether library already installed or not - install and load as needed:
apply(as.matrix(packages), MARGIN = 1, FUN = function(x) {
  
  pkg_avail <- nzchar(system.file(package = x))   # check if library is installed on system
  
  if(pkg_avail){
    require(x, character.only = TRUE)             # load the library, if already installed
    
  }else{
    install.packages(x)                           # install the library, if missing
    require(x, character.only = TRUE)             # load after installation
  }
})

## install stan (cmdstanr)
## in case you receive an error in the installation, run the following function before install cmdstanr
## https://discourse.mc-stan.org/t/fail-to-install-cmdstan-v2-35-0-with-cmdstanr-0-8-1/35431/2
# Sys.setenv("TAR"="internal")
## install it 
# install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
library("cmdstanr")

## use the following work-around so brms runs smoothly
renv::install("rstan")
packageVersion("rstan")
library(brms)
options(brms.backend = "cmdstanr")

## to make dmetar work
install.packages("MuMIn", type = "binary")
if (!require("remotes")) {
  install.packages("remotes")
}
remotes::install_github("MathiasHarrer/dmetar")


## keep the environment tidy 
rm(packages)

```

# Fig. 1 - 5

## Fig. 1

##### color

```{r}

## concave exponential functional relationship 
x <- seq(from = 2, to = 24, by = 0.01)
y <- -3*exp(-0.2*x) + 2.5

## store x and y in a df for plotting 
Fig_01.1_data <- data.frame(
  x = x, 
  y = y)

## linear functional relationship 
x <-  seq(from = 2, to = 24, by = 0.01)
y <- x/10 
## store x and y in a df for plotting 
Fig_01.2_data <- data.frame(
  x = x,
  y = y)

## convex exponential functional relationship 
x <- seq(from = 2, to = 24, by = 0.01)
y <- 2*exp(0.2*x) / 120
## store x and y in a df for plotting 
Fig_01.3_data <- data.frame(
  x = x, 
  y = y)

## create Fig. 01
Fig_01 <- ggplot(data = Fig_01.1_data, 
                 aes(x = x, 
                     y = y)) + 
  xlab(label = "sociometric status") + 
  ylab(label = "social well-being") + 
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()) + 
  ## concave 
  geom_point(data = Fig_01.1_data, 
             aes(x = x, 
                 y = y), 
             color = "#2297E6") + 
  annotate("text", label = "Delta", parse = TRUE,
           x = 10.5, y = 1.75, size = 6) +
  annotate("text", label = "1.1", 
           x = 11.25, y = 1.65, size = 3) +
  geom_segment(x = 5, y = 1.4,
               xend = 10, yend = 1.4, 
               linetype = 2) +
  geom_segment(x = 10, y = 1.4,
               xend = 10, yend = 2.1) +
  geom_point(x = 5, y = 1.4, 
             shape = 1, size = 6, color = "black") +
  geom_point(x = 5, y = 1.4, 
             shape = 16, size = 6, color = "grey") +
  geom_point(x = 10, y = 2.1, 
             shape = 16, size = 6, color = "black") +
  annotate("text", label = "Delta", parse = TRUE,
           x = 18, y = 2.3, size = 6) +
  annotate("text", label = "1.2", 
           x = 18.75, y = 2.2, size = 3) + 
  geom_segment(x = 12.5, y = 2.25,
               xend = 17.5, yend = 2.25, 
               linetype = 2) +
  geom_segment(x = 17.5, y = 2.25,
               xend = 17.5, yend = 2.4) +
  geom_point(x = 12.5, y = 2.25, 
             shape = 1, size = 6, color = "black") +
  geom_point(x = 12.5, y = 2.25, 
             shape = 16, size = 6, color = "grey") +
  geom_point(x = 17.5, y = 2.4, 
             shape = 16, size = 6, color = "black") +
  
  ## linear 
  geom_point(data = Fig_01.2_data, 
             aes(x = x, 
                 y = y), 
             color = "black") +
  annotate("text", label = "Delta", parse = TRUE,
           x = 13, y = 1, size = 6) +
  annotate("text", label = "2.1", 
           x = 13.75, y = 0.9, size = 3) +
  geom_segment(x = 7.5, y = 0.75,
               xend = 12.5, yend = 0.75, 
               linetype = 2) +
  geom_segment(x = 12.5, y = 0.75,
               xend = 12.5, yend = 1.25) +
  geom_point(x = 7.5, y = 0.75, 
             shape = 1, size = 6, color = "black") +
  geom_point(x = 7.5, y = 0.75, 
             shape = 16, size = 6, color = "grey") +
  geom_point(x = 12.5, y = 1.25, 
             shape = 16, size = 6, color = "black") +
  annotate("text", label = "Delta", parse = TRUE,
           x = 20.5, y = 1.75, size = 6) +
  annotate("text", label = "2.2", 
           x = 21.25, y = 1.65, size = 3) +
  geom_segment(x = 15, y = 1.5,
               xend = 20, yend = 1.5, 
               linetype = 2) +
  geom_segment(x = 20, y = 1.5,
               xend = 20, yend = 2) +
  geom_point(x = 15, y = 1.5, 
             shape = 1, size = 6, color = "black") +
  geom_point(x = 15, y = 1.5, 
             shape = 16, size = 6, color = "grey") +
  geom_point(x = 20, y = 2, 
             shape = 16, size = 6, color = "black") +
  
  ## convex
  geom_point(data = Fig_01.3_data, 
             aes(x = x, 
                 y = y), 
             color = "#DF536B") + 
  annotate("text", label = "Delta", parse = TRUE,
           x = 15.5, y = 0.2, size = 6) +
  annotate("text", label = "3.1", 
           x = 16.25, y = 0.1, size = 3) +
  geom_segment(x = 10, y = 0.125,
               xend = 15, yend = 0.125, 
               linetype = 2) +
  geom_segment(x = 15, y = 0.125,
               xend = 15, yend = 0.35) +
  geom_point(x = 10, y = 0.125, 
             shape = 1, size = 6, color = "black") +
  geom_point(x = 10, y = 0.125, 
             shape = 16, size = 6, color = "grey") +
  geom_point(x = 15, y = 0.35, 
             shape = 16, size = 6, color = "black") +
  annotate("text", label = "Delta", parse = TRUE,
           x = 23.05, y = 1, size = 6) +
  annotate("text", label = "3.2", 
           x = 23.8, y = 0.9, size = 3) +
  
  geom_segment(x = 17.5, y = 0.55,
               xend = 22.5, yend = 0.55, 
               linetype = 2) +
  geom_segment(x = 22.5, y = 0.55,
               xend = 22.5, yend = 1.5) +
  
  geom_point(x = 17.5, y = 0.55, 
             shape = 1, size = 6, color = "black") +
  geom_point(x = 17.5, y = 0.55, 
             shape = 16, size = 6, color = "grey") +
  geom_point(x = 22.5, y = 1.5, 
             shape = 16, size = 6, color = "black") 

## save Fig. 01
ggsave(file = "Output_Graphics/Fig_01.jpg", 
       Fig_01, 
       width = 16, 
       height = 9, 
       units = "cm", 
       dpi = 600,
       bg='#ffffff') 

Fig_01

## keep the environment tidy 
rm(x, y, Fig_01.1_data, Fig_01.2_data, Fig_01.3_data)
```

## Fig. 2a - 2c

```{r}

## concave exponential functional relationship 
y_concave <- function(x){-3*exp(-0.2*x) + 2.5}

## control group 
x <- c(5, 7.5, 10, 12.5)
y_control <- y_concave(x)
## treatment group 
x <- x + 10
y_treatment <- y_concave(x)


## create plot df 
Fig_02.1_data <- data.frame(
  CM = y_control, 
  TM = y_treatment
)

## create Fig. 0X
Fig_02.1 <- ggplot(data = Fig_02.1_data, 
                 aes(x = CM, 
                     y = TM)) + 
  geom_segment(aes(xend = CM, yend = CM), color = "grey", alpha = 1) +
  geom_point() + 
  geom_point(aes(x = CM, 
                 y = TM)) + 
  geom_abline(intercept = 0, 
              slope = 1) + 
  xlim(min(c(Fig_02.1_data$CM, Fig_02.1_data$TM)), 
       max(c(Fig_02.1_data$CM, Fig_02.1_data$TM)) ) +
  ylim(min(c(Fig_02.1_data$CM, Fig_02.1_data$TM)), 
       max(c(Fig_02.1_data$CM, Fig_02.1_data$TM)) ) +
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()) + 
  ggtitle(label = "2a")


## linear functional relationship 
y_linear <- function(x){x/10}

## control group 
x <- c(5, 7.5, 10, 12.5)
y_control <- y_linear(x)
## treatment group 
x <- x + 10
y_treatment <- y_linear(x)


## create plot df 
Fig_02.2_data <- data.frame(
  CM = y_control, 
  TM = y_treatment
)

## create Fig. 0X
Fig_02.2 <- ggplot(data = Fig_02.2_data, 
                 aes(x = CM, 
                     y = TM)) + 
  geom_segment(aes(xend = CM, yend = CM), color = "grey", alpha = 1) +
  geom_point() + 
  geom_point(aes(x = CM, 
                 y = TM)) + 
  geom_abline(intercept = 0, 
              slope = 1) + 
  xlim(min(c(Fig_02.2_data$CM, Fig_02.2_data$TM)), 
       max(c(Fig_02.2_data$CM, Fig_02.2_data$TM)) ) +
  ylim(min(c(Fig_02.2_data$CM, Fig_02.2_data$TM)), 
       max(c(Fig_02.2_data$CM, Fig_02.2_data$TM)) ) +
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()) + 
  ggtitle(label = "2b")


## convex exponential functional relationship 
y_convex <- function(x){2*exp(0.2*x) / 120}

## control group 
x <- c(5, 7.5, 10, 12.5)
y_control <- y_convex(x)
## treatment group 
x <- x + 10
y_treatment <- y_convex(x)


## create plot df 
Fig_02.3_data <- data.frame(
  CM = y_control, 
  TM = y_treatment
)

## create Fig. 0X
Fig_02.3 <- ggplot(data = Fig_02.3_data, 
                 aes(x = CM, 
                     y = TM)) + 
  geom_segment(aes(xend = CM, yend = CM), color = "grey", alpha = 1) +
  geom_point() + 
  geom_point(aes(x = CM, 
                 y = TM)) + 
  geom_abline(intercept = 0, 
              slope = 1) + 
  xlim(min(c(Fig_02.3_data$CM, Fig_02.3_data$TM)), 
       max(c(Fig_02.3_data$CM, Fig_02.3_data$TM)) ) +
  ylim(min(c(Fig_02.3_data$CM, Fig_02.3_data$TM)), 
       max(c(Fig_02.3_data$CM, Fig_02.3_data$TM)) ) +
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()) + 
  ggtitle(label = "2c")



Fig_02 <- gridExtra::grid.arrange(grobs = list(Fig_02.1, Fig_02.2, Fig_02.3), 
                        ncol = 3)

## save Fig. 02
ggsave(file = "Output_Graphics/Fig_02.jpg", 
       Fig_02, 
       width = 16, 
       height = 8, 
       dpi = 600,
       units = "cm") 

## keep the environment tidy 
rm(y_concave, y_linear, y_convex, x, y_control, y_treatment,
   Fig_02.1, Fig_02.2, Fig_02.3)

```

## Fig. 3

```{r}

### tau_CM = 0, tau_MD > 0 

## linear functional relationship 
y_linear <- function(x){x/10}

## control group 
x <- c(10, 10, 10, 10)
y_control <- y_linear(x)
## treatment group 
x <- x + c(5, 7.5, 10, 12.5)
y_treatment <- y_linear(x)

## create plot df 
Fig_03_data <- data.frame(
  CM = y_control, 
  TM = y_treatment
)

## create Fig. 03
Fig_03 <- ggplot(data = Fig_03_data, 
                 aes(x = CM, 
                     y = TM)) + 
  geom_segment(aes(xend = CM, yend = CM), color = "grey", alpha = 1) +
  geom_point() + 
  geom_point(aes(x = CM, 
                 y = TM)) + 
  geom_abline(intercept = 0, 
              slope = 1) + 
  xlim(min(c(Fig_03_data$CM, Fig_03_data$TM)), 
       max(c(Fig_03_data$CM, Fig_03_data$TM)) ) +
  ylim(min(c(Fig_03_data$CM, Fig_03_data$TM)), 
       max(c(Fig_03_data$CM, Fig_03_data$TM)) ) +
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()) 

Fig_03

## save Fig. 03
ggsave(file = "Output_Graphics/Fig_03.jpg", 
       Fig_03, 
       width = 12, 
       height = 8, 
       dpi = 600,
       units = "cm") 

## keep the environment tidy 
rm(y_linear, y_control, y_treatment, x)

```

## Fig. 4

```{r}

### tau_CM = 0, tau_MD > 0 

## concave exponential functional relationship 
y_concave <- function(x){-3*exp(-0.2*x) + 2.5}

## linear functional relationship 
y_linear <- function(x){x/10}

## control group 
# x <- c(2.5, 5, 7.5, 10, 12.5)
x <- c(2, 3, 4, 5, 6)
y_control <- y_concave(x)
## treatment group 
x <- x + 5 
y_treatment1 <- rep(max(y_concave(x)), times = length(x))
y_treatment2 <- (y_treatment1[1] - y_control[1]) + y_control

## create plot df 
Fig_04_data <- data.frame(
  CM = y_control, 
  TM1 = y_treatment1, 
  TM2 = y_treatment2
)

## create Fig. 04
Fig_04 <- ggplot() + 
  geom_abline(intercept = max(Fig_04_data$TM1), 
              slope = 0, 
              linetype = 2, 
              color = "red")+
  geom_abline(intercept = 0, 
              slope = 1) + 
  geom_segment(data = Fig_04_data,
               aes(x = CM, 
                   y = TM1, 
                   yend = TM2), 
               color = "grey", 
               linetype = 2, 
               size = 1) +
  geom_segment(data = Fig_04_data,
               aes(x = CM, 
                   y = , CM,
                   yend = TM1), 
               color = "grey", 
               size = 2) +
  geom_point(data = Fig_04_data, 
             aes(x = CM, 
                 y = TM1)) + 
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()) +
  xlim(0.4, 3.5) + 
  ylim(0.4, 3.5)

Fig_04

## save Fig. 04
ggsave(file = "Output_Graphics/Fig_04.jpg", 
       Fig_04, 
       width = 12, 
       height = 8, 
       dpi = 600,
       units = "cm") 

## keep the environment tidy 
rm(y_concave, y_linear, x, y_treatment1, y_treatment2)

```

# Methods

## Selecting Data Sets

### Prepare Data

#### Download

```{r}

## download data as rds object from DRIPHT Repository (https://osf.io/g2fzq) 
rds_download <- osfr::osf_retrieve_file("2nw6v") %>% 
  osfr::osf_download(., 
                     path = file.path("Input_Data/rds"), 
                     conflicts = "overwrite")

## import the list 
IPD_list <- readRDS(rds_download$local_path)

## store IPD per data-set as csv files 
invisible(
 sapply(
  names(IPD_list$IPD), 
  function(name){
    readr::write_csv(IPD_list$IPD[[name]], 
                 file = paste(
                   "Input_Data/", "csv/", # path 
                   paste(name, ".csv", sep = ""), # file name
                   sep = ""))
  }) 
)

## download info on multi-lab data 
rds_download <- osfr::osf_retrieve_file("cyx4v") %>% 
  osfr::osf_download(., 
                     path = file.path("Input_Data/"), 
                     conflicts = "overwrite")

## import the list 
repository_info <- readr::read_csv2(rds_download$local_path)

## keep the environment tidy 
rm(
  rds_download, 
  IPD_list
)

```

#### Import

```{r}

## collect paths 
paths <-  list.files(path = "Input_Data/csv", 
                    pattern = "\\.csv$",   
                    full.names = TRUE)

## apply read function to paths 
data_file <- lapply(paths, readr::read_csv)

## rename list objects 
names <- stringr::str_remove(
  string = list.files(path = "Input_Data/csv", 
                      pattern = "\\.csv$",
                      full.names = FALSE), 
  pattern = ".csv")
names(data_file) <- names

## keep environment tidy 
rm(paths, 
   names)

```

#### Edit Group Association

All data sets are coded to produce a positive meta-analytical mean if that effect has the same sign as the original or if the dependent variable is affected in the hypothesized direction.

```{r}

## change PSACR_002 (switch 0 and 1)
data_file$Cognitive_Reappraisal$Group <- ifelse(data_file$Cognitive_Reappraisal$Group == 1, 0, 1) 

```

#### Calculate Means, ES & SE

```{r}

### calculate control group means and MD 
### and the according standard errors 

## create site summaries 
Site_Summaries <- lapply(
  names(data_file), 
  function(name){
    
    ## pull data frame 
    data <- data_file[[name]]
    
    site_info <- data %>%
      # calculate site info 
      dplyr::group_by(Data_Collection_Site, Group) %>%
      dplyr::summarise(
        mean  = mean(DV, na.rm = TRUE),
        sd = sd(DV, na.rm = TRUE),
        n  = sum(!is.na(DV)),
        .groups = "drop"
      ) %>%
      # represent site info one row per Data_Collection_Site
      tidyr::pivot_wider(
        names_from = Group,
        values_from = c(n, mean, sd)
      )
    
    ## MD 
    site_info_MD <- metafor::escalc(
      measure = "MD",
      m1i  = mean_1, # treatment
      sd1i = sd_1,
      n1i  = n_0,
      m2i  = mean_0, # control
      sd2i = sd_0,
      n2i  = n_0,
      data = site_info
    )
    ## add SE of MD
    site_info_MD$se <- sqrt(site_info_MD$vi)
    
    ## CM 
    site_info_CM <- metafor::escalc(
      measure = "MN",
      mi  = mean_0,
      sdi = sd_0,
      ni  = n_0,
      data = site_info
    ) %>% 
      dplyr::select(!grep("_1",names(site_info)))
    
    ## add SE of CM
    site_info_CM$se <- sqrt(site_info_CM$vi)
    
    ## output df
    data.frame(
      Data_Collection_Site = site_info_MD$Data_Collection_Site, 
      MD = site_info_MD$yi, 
      SE_MD = site_info_MD$se, 
      CM = site_info_CM$yi, 
      SE_CM = site_info_CM$se,
      n_treatment = site_info_MD$n_1,
      n_control = site_info_MD$n_0
    )
    
  }
)

## rename list objects
names(Site_Summaries) <- names(data_file)

```

#### Run Two-Stage Meta-Analyses

```{r}

### MD 

## all MA except for Jacowitz_Population 
two_stage_MA_MD <- lapply(
  names(Site_Summaries)[
    -grep(pattern = "Jacowitz_Population",
          x = names(Site_Summaries))],
    # names(Site_Summaries), 
  function(MASC_name){
         # select data set 
         MASC_data <- Site_Summaries[[MASC_name]]
         # run meta-analysis 
         metafor::rma(
           yi = MD, 
           sei = SE_MD,
           data = MASC_data, 
           method = "REML" #, 
           # control=list(stepadj=0.3, verbose=TRUE)
           )
         })

## rename list objects of two_stage_MA_MD
names(two_stage_MA_MD) <- names(Site_Summaries)[
  -grep(pattern = "Jacowitz_Population", 
        x = names(Site_Summaries))]

##  MA  for Jacowitz_Population
ML1_Jacowitz_Population <- lapply(
  names(Site_Summaries)[
    grep(pattern = "Jacowitz_Population",
          x = names(Site_Summaries))],
  function(MASC_name){
         # select data set
         MASC_data <- Site_Summaries[[MASC_name]]
         # run meta-analysis
         metafor::rma(
           yi = MD,
           sei = SE_MD,
           data = MASC_data,
           method = "REML", 
           control=list(stepadj=0.3, verbose=TRUE)
         )
       })

## add Jacowitz_Population to the list
two_stage_MA_MD$Jacowitz_Population <- ML1_Jacowitz_Population[[1]]


### CM 

## all MA except for Jacowitz_Population 
two_stage_MA_CM <- lapply(
  names(Site_Summaries)[
  -grep(pattern = "Jacowitz_Population", 
        x = names(Site_Summaries))], 
  function(MASC_name){
         # select data set 
         MASC_data <- Site_Summaries[[MASC_name]]
         # run meta-analysis 
         metafor::rma(
           yi = CM, 
           sei = SE_CM,
           data = MASC_data, 
           method = "REML"
           )
         })

## rename list objects of two_stage_MA_CM
names(two_stage_MA_CM) <- names(Site_Summaries)[
  -grep(pattern = "Jacowitz_Population", 
        x = names(Site_Summaries))]

##  MA  for Jacowitz_Population 
ML1_Jacowitz_Population <- lapply(
  names(Site_Summaries)[
    grep(pattern = "Jacowitz_Population", 
          x = names(Site_Summaries))],
  function(MASC_name){
         # select data set 
         MASC_data <- Site_Summaries[[MASC_name]]
         # run meta-analysis 
         metafor::rma(
           yi = CM, 
           sei = SE_CM,
           data = MASC_data, 
           method = "REML",
           control=list(stepadj=0.3, verbose=TRUE)
         )
       })

## add Jacowitz_Population to the list 
two_stage_MA_CM$Jacowitz_Population <- ML1_Jacowitz_Population[[1]]

rm(ML1_Jacowitz_Population)

```

## Table 2

### Data sets for goals (1) and (2)

#### Analysis Based Exclusions

```{r}

## identify which data sets contain heterogeneous effects 
which_to_exclude <- data.frame(
  Data_Set = names(two_stage_MA_MD), 
  Effect_Homogeneity = unlist(lapply(
    names(two_stage_MA_MD),
    function(name){
      ifelse(test = two_stage_MA_MD[[name]]$QEp >= 0.05,
             yes = "yes", 
             no = "no")
      }))
  )

## names of excluded effects 
homogeneous <- as.vector(unlist(
  which_to_exclude %>% 
    dplyr::filter(Effect_Homogeneity == "yes") %>% 
    dplyr::select(Data_Set)))

## names of included effects 
included_heterogeneous <- dplyr::setdiff(which_to_exclude$Data_Set, homogeneous)

## homogeneity based exclusions 
length(which(which_to_exclude$Effect_Homogeneity == "yes"))

## n included 
length(included_heterogeneous)

## n excluded: homogeneous effects 
length(homogeneous)


```

#### Design Based Exclusions

The decisions about design are recorded in a table provided on OSF:

```{r}

### selecting quantitative independent variables 

quantitative <- c(
  ## control group designs 
  "Oppenheimer_Meyvis", 
  "Risen_CR", 
  "Risen", 
  "Gray",
  "Sripada",
  ## reference group designs 
  "Monin", ## differing opinions on the quantitativeness
  "Ross3", ## differing opinions on the quantitativeness
  "Hsee", 
  "Jacowitz_Births", 
  "Jacowitz_Distance", 
  "Jacowitz_Height", 
  "Jacowitz_Population",
  "Lorge",
  "Oppenheimer_Monin", 
  "Critcher",
  "Huang_CR", 
  "Huang"
)

qualitative <- dplyr::setdiff(included_heterogeneous, quantitative)

## other designs for which the analytic framework did not match 
other_exclusions <- c(
  "Huang", 
  "Hsee"
)

included_designs <- quantitative[!quantitative %in% other_exclusions]
included_designs <- included_designs[included_designs %in% included_heterogeneous]

## n included (quantitative)
length(included_designs)

```

#### Identifying Control Condition Designs and Reference Condition Designs

The decisions about design are recorded in a table provided on OSF:

```{r}

## create vector with designs with control groups 
control_condition <- c(
    # "Oppenheimer_Meyvis", # homogeneous 
    # "Risen_CR", # homogeneous 
    "Risen", 
    "Gray",
    "Sripada"
)

## create vector with reference group designs 
reference_condition <- dplyr::setdiff(included_designs, control_condition)

## n control_condition
length(control_condition)

## n control_condition
length(reference_condition)

```

### Create Table 2

```{r}

## change the underscores to match the table 
all_designs_ID <- c(control_condition, reference_condition)

all_designs_repoID <- unlist(lapply(
  1:length(all_designs_ID), 
  function(x){
    repository_info$Repository_ID[
      which(sub(".*__", 
                "", 
                repository_info$Repository_ID) %in% all_designs_ID[x])]
  }
))


## table with repository info: https://osf.io/cyx4v 
all_designs <- lapply(
  all_designs_repoID, 
  function(ID){
    repository_info %>% 
      dplyr::filter(Repository_ID == ID)}
  )
## create df 
all_designs <- do.call(rbind, all_designs)

## create Table 2
Table_2 <- data.frame(
  ID = c(1:nrow(all_designs)),
  Design = c(rep("control condition", times = length(control_condition)),
             rep("reference condition", times = length(reference_condition))),
  Project = all_designs$Project,
  Origina_Authors = all_designs$Orig_Authors,
  Items_n = all_designs$Items_n,
  Scale_Min = all_designs$Scale_Min,
  Scale_Max = all_designs$Scale_Max
)

## export table as csv
readr::write_csv(Table_2, file = "Output_Tables/table_2.csv")

## export table as .docx
officer::read_docx() %>%
  flextable::body_add_flextable(
    value = flextable::flextable(data = Table_2)) %>%
  print(target = "Output_Tables/table_2.docx")

## show table 
Table_2

```

## Table 3

### Data sets for goal (3)

#### Analysis Based Exclusions

```{r}


## identify which data sets contain heterogeneous effects 
which_to_include <- data.frame(
  Data_Set = names(two_stage_MA_MD), 
  Effect_Homogeneity = unlist(lapply(
    names(two_stage_MA_MD),
    function(name){
      ifelse(test = two_stage_MA_MD[[name]]$QEp >= 0.05,
             yes = "yes", 
             no = "no")
      })), 
  Non_Null = unlist(lapply(
    names(two_stage_MA_MD),
    function(name){
      ifelse(test = two_stage_MA_MD[[name]]$pval < 0.05,
             yes = "yes", 
             no = "no")
      }))
  )

## names of included effects 
homogeneous_nonnull <- as.vector(unlist(
  which_to_include %>% 
    dplyr::filter(Effect_Homogeneity == "yes") %>% 
    dplyr::filter(Non_Null == "yes") %>% 
    dplyr::select(Data_Set)))

## names of excluded effects 
excluded <- dplyr::setdiff(which_to_include$Data_Set, homogeneous)


## n included 
length(homogeneous_nonnull)

## n excluded: 
length(excluded)

```

#### Design Based Exclusions

The decisions about design are recorded in a table provided on OSF:

```{r}

### selecting quantitative independent variables 

quantitative_homogeneous_nonnull <- c(
  ## control group designs 
  "Dang2017",
  "Oppenheimer_Meyvis", 
  "Risen_CR", 
  ## reference group designs 
  "Monin", ## differing opinions on the quantitativeness
  "Ross3" ## differing opinions on the quantitativeness
)

qualitative_homogeneous_nonnull <- dplyr::setdiff(
  homogeneous_nonnull,
  quantitative_homogeneous_nonnull)

## other designs for which the analytic framework did not match 
other_exclusions <- c(
  "Ross1", # not an experimental design 
  "Huang"
)

included_designs_homogeneous_nonnull <- quantitative[!quantitative %in% other_exclusions]
included_designs_homogeneous_nonnull <- included_designs[included_designs %in% homogeneous_nonnull]

## n included (quantitative)
length(included_designs_homogeneous_nonnull)

```

#### Identifying Control Condition Designs and Reference Condition Designs

The decisions about design are recorded in a table provided on OSF:

```{r}

## create vector with designs with control groups 
control_condition_homogeneous_nonnull <- c(
    "Oppenheimer_Meyvis", # homogeneous
    "Risen_CR", # homogeneous
    "Dang2017"
)

included_homogeneous_nonnull <- dplyr::intersect(
  homogeneous_nonnull, 
  control_condition_homogeneous_nonnull)

## n control_condition
length(included_homogeneous_nonnull)

```

### Create Table 3

Homogeneous Non-Null

```{r}

included_homogeneous_nonnull_repoID <- unlist(lapply(
  1:length(included_homogeneous_nonnull), 
  function(x){
    repository_info$Repository_ID[
      which(sub(".*__", 
                "", 
                repository_info$Repository_ID) %in% included_homogeneous_nonnull[x])]
  }
))

## table with repository info: https://osf.io/cyx4v 
homogeneous_nonnull_designs <- lapply(
  included_homogeneous_nonnull_repoID, 
  function(ID){
    repository_info %>% 
      dplyr::filter(Repository_ID == ID)}
  )
## create df 
homogeneous_nonnull_designs <- do.call(rbind, homogeneous_nonnull_designs)

## create Table 3
Table_3 <- data.frame(
  ID = c(1:nrow(homogeneous_nonnull_designs))+nrow(all_designs),
  Design = rep("control condition", times = nrow(homogeneous_nonnull_designs)),
  Project = homogeneous_nonnull_designs$Project,
  Origina_Authors = homogeneous_nonnull_designs$Orig_Authors,
  Items_n = homogeneous_nonnull_designs$Items_n,
  Scale_Min = homogeneous_nonnull_designs$Scale_Min,
  Scale_Max = homogeneous_nonnull_designs$Scale_Max
)

## export table as csv
readr::write_csv(Table_3, file = "Output_Tables/table_3.csv")

## export table as .docx
officer::read_docx() %>%
  flextable::body_add_flextable(
    value = flextable::flextable(data = Table_3)) %>%
  print(target = "Output_Tables/table_3.docx")

## show table 
Table_3

```

## Descriptors

### For goals (1) and (2)

#### tau_MD

```{r}

tau_MD <- lapply(
  all_designs_ID, 
  function(name){
    data.frame(
      data_set = name, 
      tau_MD = round(sqrt(two_stage_MA_MD[[name]]$tau2), digits = 3), 
      decision = ifelse(two_stage_MA_MD[[name]]$QEp < 0.05, ">0", "→0")
    )
  }
)

tau_MD_df <- do.call(rbind, tau_MD)

```

#### tau_CM

```{r}

tau_CM <- lapply(
  all_designs_ID, 
  function(name){
    ## create summary file (for easy access)
    summary_file <- two_stage_MA_CM[[name]]
    
    data.frame(
      data_set = name, 
      tau_CM = round(sqrt(two_stage_MA_CM[[name]]$tau2), digits = 3), 
      decision = ifelse(two_stage_MA_CM[[name]]$QEp < 0.05, ">0", "→0")
    )
  }
)

tau_CM_df <- do.call(rbind, tau_CM)

```

#### Run One-Stage Meta-Analyses

By default, these chunk only imports the files. If you wish to re-run the brms models, remove the \# in the following chunks

```{r}

## run the full model
full_model_brms <- lapply(
  all_designs_ID,
  function(name){
    # random intercepts & random slopes
    brms::brm(
      brms::bf(
        formula = DV ~ Group + (Group | Data_Collection_Site),
        decomp = "QR"),
      data = data_file[[name]],
      cores = 4,
      backend = "cmdstanr")
    })

## rename list objects
names(full_model_brms) <- all_designs_ID

## export results
readr::write_rds(full_model_brms, "Output_Data/heterogeneous_brms.rds")

## import results: if the data exist, this saves a lot of time
full_model_brms <- readr::read_rds("Output_Data/heterogeneous_brms.rds")

```

#### ISC

```{r}

ISC_decision <- lapply(
  all_designs_ID, 
  function(name){
    ## create summary file (for easy access)
    summary_file <- summary(full_model_brms[[name]])$random$Data_Collection_Site
    
    ## identify if the interval includes the null, and if ISC is smaller or larger than zero 
    non_zero_ISC <- if (
      sign(summary_file["cor(Intercept,Group)", "l-95% CI"]) == 
      sign(summary_file["cor(Intercept,Group)", "u-95% CI"]) & 
      sign(summary_file["cor(Intercept,Group)", "Estimate"]) > 0
    ) {
      ifelse(summary_file["cor(Intercept,Group)", "Estimate"] > 0.75, "→1", ">0") 
    } else if (
      sign(summary_file["cor(Intercept,Group)", "l-95% CI"]) == 
      sign(summary_file["cor(Intercept,Group)", "u-95% CI"]) & 
      sign(summary_file["cor(Intercept,Group)", "Estimate"]) < 0
    ) {
      ifelse(summary_file["cor(Intercept,Group)", "Estimate"] < -0.75, "→-1", "<0") 
    } else if (
      sign(summary_file["cor(Intercept,Group)", "l-95% CI"]) != 
      sign(summary_file["cor(Intercept,Group)", "u-95% CI"])
    ) {
      "→0"
    }
    data.frame(
      data_set = name, 
      parameter = round(summary_file["cor(Intercept,Group)", "Estimate"], digits = 3),
      decision = non_zero_ISC
    )
  }
)

ISC_df <- do.call(rbind, ISC_decision)

```

#### rank correlation Kendall's tau

```{r}

library(Kendall)  # for Kendall's tau-b

library(posterior)

kendalls_tau_b_decision <- lapply(
  all_designs_ID, 
  function(name){
    
    draws <- brms::as_draws_df(full_model_brms[[name]])
    
    # get site names
    re_cols <- grep("^r_Data_Collection_Site\\[", names(draws), value = TRUE)
    site_names <- unique(sub("^r_Data_Collection_Site\\[([^,]+),.*$", "\\1", re_cols))
    
    kendalls_tau_b_draws <- numeric(nrow(draws))
    
    for (i in seq_len(nrow(draws))) {
      
      CM <- numeric(length(site_names))
      TM <- numeric(length(site_names))
      
      for (j in seq_along(site_names)) {
        site <- site_names[j]
        
        cm_name <- paste0("r_Data_Collection_Site[", site, ",Intercept]")
        md_name <- paste0("r_Data_Collection_Site[", site, ",Group]")  # adjust name
        
        CM[j] <- draws$b_Intercept[i] + draws[[cm_name]][i]
        MD_j  <- draws$b_Group[i] + draws[[md_name]][i]
        
        TM[j] <- CM[j] + MD_j
      }
      
      kendalls_tau_b_draws[i] <- Kendall::Kendall(CM, TM)$tau
    }
    
    # kendalls_tau_b_draws
    
    kendalls_tau_b_quantiles <- quantile(kendalls_tau_b_draws, c(0.025, 0.5, 0.975))
    
    ## identify if the interval includes the null 
    non_zero_kendalls_tau_b <- ifelse(sign(kendalls_tau_b_quantiles[1]) == 
                                        sign(kendalls_tau_b_quantiles[3]), 
                                      yes = "yes",
                                      no = "no")
    
    non_zero_kendalls_tau_b <- if (
      sign(kendalls_tau_b_quantiles[1]) == 
      sign(kendalls_tau_b_quantiles[3]) & 
      sign(mean(kendalls_tau_b_draws)) > 0
    ) {
      ifelse(mean(kendalls_tau_b_draws) > 0.75, "→1", ">0") 
    } else if (
      sign(kendalls_tau_b_quantiles[1]) == 
      sign(kendalls_tau_b_quantiles[3]) & 
      sign(mean(kendalls_tau_b_draws)) < 0
    ) {
      ifelse(mean(kendalls_tau_b_draws) < -0.75, "→-1", "<0") 
    } else if (
      sign(kendalls_tau_b_quantiles[1]) != 
      sign(kendalls_tau_b_quantiles[3])
    ) {
      "→0"
    }
   
    data.frame(
      data_set = name, 
      parameter = mean(kendalls_tau_b_draws), 
      decision = non_zero_kendalls_tau_b
    )
     
  }
  
)

tau_b_df <- do.call(rbind, kendalls_tau_b_decision)


```

### ISC\^2

```{r}


ISC2 <- lapply(
  all_designs_ID, 
  function(name){
    ## create summary file (for easy access)
    summary_file <- summary(full_model_brms[[name]])$random$Data_Collection_Site
    
    data.frame(
      data_set = name, 
      ISC2 = round(summary_file["cor(Intercept,Group)", "Estimate"]^2, digits = 3)
    )
  }
)

ISC2_df <- do.call(rbind, ISC2)


```

### For goal (3)

#### tau_MD

```{r}

tau_MD <- lapply(
  included_homogeneous_nonnull, 
  function(name){
    data.frame(
      data_set = name, 
      tau_MD = round(sqrt(two_stage_MA_MD[[name]]$tau2), digits = 3), 
      decision = ifelse(two_stage_MA_MD[[name]]$QEp < 0.05, ">0", "→0")
    )
  }
)

tau_MD_df_3 <- do.call(rbind, tau_MD)

```

#### tau_CM

```{r}

tau_CM <- lapply(
  included_homogeneous_nonnull, 
  function(name){
    ## create summary file (for easy access)
    summary_file <- two_stage_MA_CM[[name]]
    
    data.frame(
      data_set = name, 
      tau_CM = round(sqrt(two_stage_MA_CM[[name]]$tau2), digits = 3), 
      decision = ifelse(two_stage_MA_CM[[name]]$QEp < 0.05, ">0", "→0")
    )
  }
)

tau_CM_df_3 <- do.call(rbind, tau_CM)

```

#### Run One-Stage Meta-Analyses

By default, these chunk only imports the files. If you wish to re-run the brms models, remove the \# in the following chunks

```{r}

## run the full model
homogeneous_nonnull_brms <- lapply(
  included_homogeneous_nonnull,
  function(name){
    # random intercepts & random slopes
    brms::brm(
      brms::bf(
        formula = DV ~ Group + (Group | Data_Collection_Site),
        decomp = "QR"),
      data = data_file[[name]],
      cores = 4,
      backend = "cmdstanr")
    })

## rename list objects
names(homogeneous_nonnull_brms) <- included_homogeneous_nonnull

## export results
readr::write_rds(homogeneous_nonnull_brms, "Output_Data/homogeneous_nonnull_brms.rds")

## import results: if the data exist, this saves a lot of time
homogeneous_nonnull_brms <- readr::read_rds("Output_Data/homogeneous_nonnull_brms.rds")

```

#### ISC

```{r}

ISC_decision <- lapply(
  included_homogeneous_nonnull, 
  function(name){
    ## create summary file (for easy access)
    summary_file <- summary(homogeneous_nonnull_brms[[name]])$random$Data_Collection_Site
    
    ## identify if the interval includes the null, and if ISC is smaller or larger than zero 
    non_zero_ISC <- if (
      sign(summary_file["cor(Intercept,Group)", "l-95% CI"]) == 
      sign(summary_file["cor(Intercept,Group)", "u-95% CI"]) & 
      sign(summary_file["cor(Intercept,Group)", "Estimate"]) > 0
    ) {
      ifelse(summary_file["cor(Intercept,Group)", "Estimate"] > 0.75, "→1", ">0") 
    } else if (
      sign(summary_file["cor(Intercept,Group)", "l-95% CI"]) == 
      sign(summary_file["cor(Intercept,Group)", "u-95% CI"]) & 
      sign(summary_file["cor(Intercept,Group)", "Estimate"]) < 0
    ) {
      ifelse(summary_file["cor(Intercept,Group)", "Estimate"] < -0.75, "→-1", "<0") 
    } else if (
      sign(summary_file["cor(Intercept,Group)", "l-95% CI"]) != 
      sign(summary_file["cor(Intercept,Group)", "u-95% CI"])
    ) {
      "→0"
    }
    data.frame(
      data_set = name, 
      parameter = round(summary_file["cor(Intercept,Group)", "Estimate"], digits = 3),
      decision = non_zero_ISC
    )
  }
)

ISC_df_3 <- do.call(rbind, ISC_decision)

```

#### rank correlation Kendall's tau

```{r}

library(Kendall)  # for Kendall's tau-b

library(posterior)

kendalls_tau_b_decision <- lapply(
  included_homogeneous_nonnull, 
  function(name){
    
    draws <- brms::as_draws_df(homogeneous_nonnull_brms[[name]])
    
    # get site names
    re_cols <- grep("^r_Data_Collection_Site\\[", names(draws), value = TRUE)
    site_names <- unique(sub("^r_Data_Collection_Site\\[([^,]+),.*$", "\\1", re_cols))
    
    kendalls_tau_b_draws <- numeric(nrow(draws))
    
    for (i in seq_len(nrow(draws))) {
      
      CM <- numeric(length(site_names))
      TM <- numeric(length(site_names))
      
      for (j in seq_along(site_names)) {
        site <- site_names[j]
        
        cm_name <- paste0("r_Data_Collection_Site[", site, ",Intercept]")
        md_name <- paste0("r_Data_Collection_Site[", site, ",Group]")  # adjust name
        
        CM[j] <- draws$b_Intercept[i] + draws[[cm_name]][i]
        MD_j  <- draws$b_Group[i] + draws[[md_name]][i]
        
        TM[j] <- CM[j] + MD_j
      }
      
      kendalls_tau_b_draws[i] <- Kendall::Kendall(CM, TM)$tau
    }
    
    # kendalls_tau_b_draws
    
    kendalls_tau_b_quantiles <- quantile(kendalls_tau_b_draws, c(0.025, 0.5, 0.975))
    
    ## identify if the interval includes the null 
    non_zero_kendalls_tau_b <- ifelse(sign(kendalls_tau_b_quantiles[1]) == 
                                        sign(kendalls_tau_b_quantiles[3]), 
                                      yes = "yes",
                                      no = "no")
    
    non_zero_kendalls_tau_b <- if (
      sign(kendalls_tau_b_quantiles[1]) == 
      sign(kendalls_tau_b_quantiles[3]) & 
      sign(mean(kendalls_tau_b_draws)) > 0
    ) {
      ifelse(mean(kendalls_tau_b_draws) > 0.75, "→1", ">0") 
    } else if (
      sign(kendalls_tau_b_quantiles[1]) == 
      sign(kendalls_tau_b_quantiles[3]) & 
      sign(mean(kendalls_tau_b_draws)) < 0
    ) {
      ifelse(mean(kendalls_tau_b_draws) < -0.75, "→-1", "<0") 
    } else if (
      sign(kendalls_tau_b_quantiles[1]) != 
      sign(kendalls_tau_b_quantiles[3])
    ) {
      "→0"
    }
   
    data.frame(
      data_set = name, 
      parameter = mean(kendalls_tau_b_draws), 
      decision = non_zero_kendalls_tau_b
    )
     
  }
  
)

tau_b_df_3 <- do.call(rbind, kendalls_tau_b_decision)


```

### ISC\^2

```{r}


ISC2 <- lapply(
  included_homogeneous_nonnull, 
  function(name){
    ## create summary file (for easy access)
    summary_file <- summary(homogeneous_nonnull_brms[[name]])$random$Data_Collection_Site
    
    data.frame(
      data_set = name, 
      ISC2 = round(summary_file["cor(Intercept,Group)", "Estimate"]^2, digits = 3)
    )
  }
)

ISC2_df_3 <- do.call(rbind, ISC2)


```

# Results

## Table 4

```{r}

descriptor_decisions <- data.frame(
  ID = 1:nrow(tau_MD_df), 
  data_set = tau_MD_df$data_set, 
  tau_MD = tau_MD_df$decision, 
  tau_CM = tau_CM_df$decision, 
  ISC = ISC_df$decision,
  tau_b = tau_b_df$decision
  )

descriptor_parameters <- data.frame(
  ID = 1:nrow(tau_MD_df),
  data_set = tau_MD_df$data_set, 
  tau_MD = tau_MD_df$tau_MD, 
  tau_CM = tau_CM_df$tau_CM,
  ISC = ISC_df$parameter, 
  tau_b = round(tau_b_df$parameter, digits = 3))

Table_4_list <- lapply(1:nrow(descriptor_decisions), 
             function(x){
                 rbind(
                     descriptor_parameters[x,], 
                     descriptor_decisions[x,]
                 )
             })

Table_4 <- do.call(rbind, Table_4_list)


## export table as csv
readr::write_csv(Table_4, file = "Output_Tables/table_4.csv")

## export table as .docx
officer::read_docx() %>%
  flextable::body_add_flextable(
    value = flextable::flextable(data = Table_4)) %>%
  print(target = "Output_Tables/table_4.docx")

## show table 
Table_4


```

## Fig. 5a - 5d

```{r}

## include only interesting 

selection <- c("Risen", 
               "Gray",
               "Jacowitz_Height",
               "Oppenheimer_Monin"
               )

indexing_helper <- data.frame(
  names = selection, 
  plot_indexing = c("5a", "5b", "5c", "5d")
)

Fig_05_list <- lapply(
  selection,
  function(name){
    
    ## store posterior draws as df
    posterior_draws <- as.data.frame(full_model_brms[[name]]$fit)
  
    ## create plot df 
    Fig_05_data <- data.frame(
      CM = mean(posterior_draws$b_Intercept) + 
        colMeans(posterior_draws[,grep(pattern = ",Intercept]", x = names(posterior_draws))]),
      TM = mean(posterior_draws$b_Intercept) + 
        colMeans(posterior_draws[,grep(pattern = ",Intercept]", x = names(posterior_draws))]) +
        mean(posterior_draws$b_Group) + 
        colMeans(posterior_draws[,grep(pattern = ",Group]", x = names(posterior_draws))])
      )
    
    plot_letter <- indexing_helper %>% 
  dplyr::filter(names == name) %>% 
  dplyr::select(plot_indexing)
    
    ## create Fig. 05.1
    ggplot(data = Fig_05_data, 
           aes(x = CM, 
               y = TM)) + 
      geom_segment(aes(xend = CM, yend = CM), color = "grey", alpha = 1) +
      geom_point() + 
      geom_point(aes(x = CM, 
                 y = TM)) + 
      geom_abline(intercept = 0, 
              slope = 1) + 
      xlim(min(c(Fig_05_data$CM, Fig_05_data$TM)), 
           max(c(Fig_05_data$CM, Fig_05_data$TM)) ) +
      ylim(min(c(Fig_05_data$CM, Fig_05_data$TM)), 
           max(c(Fig_05_data$CM, Fig_05_data$TM)) ) +
      theme_minimal() + 
      ggtitle(label = plot_letter)
  }
)


Fig_05 <- gridExtra::grid.arrange(grobs = Fig_05_list, 
                        ncol = 2)

## save Fig. 05
ggsave(file = "Output_Graphics/Fig_05.jpg", 
       Fig_05, 
       width = 16, 
       height = 8, 
       dpi = 600,
       units = "cm") 

## keep the environment tidy 
rm()


```

## Fig. 6

```{r}


## add ID column 
ISC2_df$ID <- as.factor(1:nrow(ISC2_df))

## create plot 
Fig_06 <- ggplot(ISC2_df, aes(x = ISC2 * 100,
                    y = forcats::fct_rev(factor(ID, 
                                                levels = ID)))) +
  geom_bar(stat = "identity", 
           width = 0.5, 
           color = "#2297E6", 
           fill = "#2297E6") +
  xlim(0, 100) +
  xlab("Amount of Heterogeneity in %") +
  ylab("Data Set") +
  theme_minimal()

## save Fig. 06
ggsave(file = "Output_Graphics/Fig_06.jpg", 
       Fig_06, 
       width = 16, 
       height = 8, 
       dpi = 600,
       units = "cm") 

Fig_06

## max, min, median
rbind(
  ISC2_df[which(ISC2_df$ISC2 == max(ISC2_df$ISC2)),], 
  ISC2_df[which(ISC2_df$ISC2 == min(ISC2_df$ISC2)),], 
  data.frame(
  data_set = "median", 
  ISC2 = median(ISC2_df$ISC2), 
  ID = 99)
)

## keep the environment tidy 
rm()

```

'

## Table 5

```{r}

descriptor_decisions <- data.frame(
  ID = 1:nrow(tau_MD_df_3)+nrow(tau_MD_df), 
  data_set = tau_MD_df_3$data_set, 
  tau_MD = tau_MD_df_3$decision, 
  tau_CM = tau_CM_df_3$decision, 
  ISC = ISC_df_3$decision,
  tau_b = tau_b_df_3$decision
  )

descriptor_parameters <- data.frame(
  ID = 1:nrow(tau_MD_df_3), 
  data_set = tau_MD_df_3$data_set, 
  tau_MD = tau_MD_df_3$tau_MD, 
  tau_CM = tau_CM_df_3$tau_CM,
  ISC = ISC_df_3$parameter, 
  tau_b = round(tau_b_df_3$parameter, digits = 3))

Table_5_list <- lapply(1:nrow(descriptor_decisions), 
             function(x){
                 rbind(
                     descriptor_parameters[x,], 
                     descriptor_decisions[x,]
                 )
             })

Table_5 <- do.call(rbind, Table_5_list)

## export table as csv
readr::write_csv(Table_5, file = "Output_Tables/table_5.csv")

## export table as .docx
officer::read_docx() %>%
  flextable::body_add_flextable(
    value = flextable::flextable(data = Table_5)) %>%
  print(target = "Output_Tables/table_5.docx")

## show table 
Table_5

```

## Fig. 7a - 7c

```{r}

## create df for plot index
included_homogeneous_nonnull_df <- data.frame(
  names = included_homogeneous_nonnull, 
  plot_indexing = c("7a", "7b", "7c")
)

## create the three plots
Fig_07_list <- lapply(
  included_homogeneous_nonnull,
  function(name){
    
    ## store posterior draws as df
    posterior_draws <- as.data.frame(homogeneous_nonnull_brms[[name]]$fit)
  
    ## create plot df 
    Fig_07_data <- data.frame(
      CM = mean(posterior_draws$b_Intercept) + 
        colMeans(posterior_draws[,grep(pattern = ",Intercept]", x = names(posterior_draws))]),
      TM = mean(posterior_draws$b_Intercept) + 
        colMeans(posterior_draws[,grep(pattern = ",Intercept]", x = names(posterior_draws))]) +
        mean(posterior_draws$b_Group) + 
        colMeans(posterior_draws[,grep(pattern = ",Group]", x = names(posterior_draws))])
      )
    
    plot_letter <- included_homogeneous_nonnull_df %>% 
      dplyr::filter(names == name) %>% 
      dplyr::select(plot_indexing)
    
    
    ## create Fig. 07.X
    ggplot(data = Fig_07_data, 
           aes(x = CM, 
               y = TM)) + 
      geom_segment(aes(xend = CM, yend = CM), color = "grey", alpha = 1) +
      geom_point() + 
      geom_point(aes(x = CM, 
                 y = TM)) + 
      geom_abline(intercept = 0, 
              slope = 1) + 
      xlim(min(c(Fig_07_data$CM, Fig_07_data$TM)), 
           max(c(Fig_07_data$CM, Fig_07_data$TM)) ) +
      ylim(min(c(Fig_07_data$CM, Fig_07_data$TM)), 
           max(c(Fig_07_data$CM, Fig_07_data$TM)) ) +
      theme_minimal() + 
      ggtitle(label = plot_letter)
  }
)

## combine plots 7a-7c
Fig_07 <- gridExtra::grid.arrange(grobs = Fig_07_list, 
                        ncol = 3)

## save Fig. 07
ggsave(file = "Output_Graphics/Fig_07.jpg", 
       Fig_07, 
       width = 16, 
       height = 8, 
       dpi = 600,
       units = "cm") 

## keep the environment tidy 
rm()


```

# General Discussion

## Reference Group & Experimental Conditions

```{r}

## identify ML2 data sets 
M2_data_sets <- as.vector(unlist(na.omit(unlist(
  lapply(
    names(data_file), 
    function(name){
        unique(ifelse(data_file[[name]]$MultiLab == "ML2", name, NA))
    }
)))))

## merge data into a single df
Merged_Site_Summaries <- do.call(rbind, Site_Summaries[M2_data_sets])

## typical sample size per replication site
mean(unlist(Merged_Site_Summaries %>% 
              dplyr::select(n_control)), na.rm = TRUE) + 
  mean(unlist(Merged_Site_Summaries %>% 
                dplyr::select(n_treatment)), na.rm = TRUE)

# ## typical number of replications (k)
mean(unlist(lapply(
    names(Site_Summaries[M2_data_sets]), 
    function(x){
        length(unique(
            Site_Summaries[[x]]$Data_Collection_Site
        ))
    }
)))


## Power for heterogeneity 
power_fun <- function(k, n, SD, tau, alpha){
  
  SD_i <- rep(SD, times = k)
  
  standard_error <- SD_i / sqrt(n) 
  
  w_i <- 1 / (standard_error^2 + tau^2)
  
  S_1 <- sum(w_i^1)
  S_2 <- sum(w_i^2)
  S_3 <- sum(w_i^3)
  
  E_Q <- (k-1) + (S_1 - S_2/S_1) * tau^2
  
  Var_Q <- 2 * (k-1) + 4 * (S_1 - S_2/S_1) * tau^2 + 2 * (S_2 - 2 * S_3/S_1 + (S_2^2)/(S_1^2) ) * tau^4
  
  r_tau2 <- E_Q^2 / Var_Q
  lambda_tau2 <- E_Q / Var_Q
  
  df <- k-1
  r <- r_tau2
  lambda <- lambda_tau2
  
  c <- qchisq(1-alpha, df = df)
  
  ## Power
  pgamma(c, shape = r, rate = lambda, lower.tail = FALSE)
  
}

## calcualte I^2 
I2_fun <- function(SD, tau, k, n){
  
  SD_i <- rep(SD, times = k)
  
  standard_error <- SD_i / sqrt(n) 
  
  # w_i <- 1 / (standard_error^2 + tau^2)
  w_i <- standard_error^-2
  
  v_tilde <- (k-1) * sum(w_i) / ( sum(w_i)^2 - sum(w_i^2))
  
  ## I^2
  tau^2 / (tau^2 + v_tilde)
}

## calculate power for two group design 
round(
  power_fun(
  k = 57, 
  n = 102, 
  SD = 1.215, 
  tau = 0.2, 
  alpha = 0.05), 
  digits = 3
)

## calculate I^2 for two group design 
round(
  I2_fun(SD = 1.215, tau = 0.2, k = 57, n = 102), 
  digits = 3)

## calculate power for remaining data of a three group design 
round(
  power_fun(
  k = 57, 
  n = 68, 
  SD = 1.215, 
  tau = 0.2, 
  alpha = 0.05), 
  digits = 3
)

## calculate I^2 for remaining data of a three group design 
round(
  I2_fun(SD = 1.215, tau = 0.2, k = 57, n = 68), 
  digits = 3)


```

# Digital Appendix

## Fig. A1

```{r}

## include all

Fig_A1_list <- lapply(
  all_designs_ID,
  function(name){
    
    ## store posterior draws as df
    posterior_draws <- as.data.frame(full_model_brms[[name]]$fit)
  
    ## create plot df 
    Fig_A1_data <- data.frame(
      CM = mean(posterior_draws$b_Intercept) + 
        colMeans(posterior_draws[,grep(pattern = ",Intercept]", x = names(posterior_draws))]),
      TM = mean(posterior_draws$b_Intercept) + 
        colMeans(posterior_draws[,grep(pattern = ",Intercept]", x = names(posterior_draws))]) +
        mean(posterior_draws$b_Group) + 
        colMeans(posterior_draws[,grep(pattern = ",Group]", x = names(posterior_draws))])
      )
    
    ## create Fig. A.1
    ggplot(data = Fig_A1_data, 
           aes(x = CM, 
               y = TM)) + 
      geom_segment(aes(xend = CM, yend = CM), color = "grey", alpha = 1) +
      geom_point() + 
      geom_point(aes(x = CM, 
                 y = TM)) + 
      geom_abline(intercept = 0, 
              slope = 1) + 
      xlim(min(c(Fig_A1_data$CM, Fig_A1_data$TM)), 
           max(c(Fig_A1_data$CM, Fig_A1_data$TM)) ) +
      ylim(min(c(Fig_A1_data$CM, Fig_A1_data$TM)), 
           max(c(Fig_A1_data$CM, Fig_A1_data$TM)) ) +
      theme_minimal() 
  }
)


Fig_A1 <- gridExtra::grid.arrange(grobs = Fig_A1_list, 
                        ncol = 3)

## save Fig. A1
ggsave(file = "Output_Graphics/Fig_A1.jpg", 
       Fig_A1, 
       width = 16, 
       height = 16, 
       dpi = 600,
       units = "cm") 

## keep the environment tidy 
rm()


```
